Blueprint for efficient nuclear spin characterization with color center

### 2024-03-27 arxiv/arxiv_main.tex
??

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\vvv}[1]{\textcolor{blue}{#1}}
%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}
\begin{document}

@@

\title{On readout and initialisation fidelity by finite demolition single shot readout}% Force line breaks with \\
%\thanks{A footnote to the article title}%

\author{Majid Zahedian}
 \affiliation{3rd physical institute University of Stuttgart, Germany}
  \affiliation{Friedrich-Alexander-Universit\"at Erlangen-N\"urnberg, Germany}%Lines b%Lines break automatically or can be forced with \\

\author{Max Keller}
 \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break automatically or can be forced with \\

\author{Minsik Kwon}
 \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break 
  \affiliation{Max Planck Institute for solid state physics, Stuttgart, Germany}%Lines break automatically or can be forced with \\

 \author{Javid Javadzade}
 \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break automatically or can be forced with \\

\author{Jonas Meinel}
 \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break 
  \affiliation{Max Planck Institute for solid state physics, Stuttgart, Germany}%Lines break automatically or can be forced with \\

\author{Vadim Vorobyov}
\email[]{v.vorobyov@pi3.uni-stuttgart.de}
 \affiliation{3rd physical institute University of Stuttgart, Germany}  
% with \\

\author{J\"org Wrachtrup}
 \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break 
 \affiliation{Max Planck Institute for solid state physics, Stuttgart, Germany}%Lines break 
 %automatically or can be forced with \\ Third institution, the second for Charlie Author

>>>>

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}
\usepackage{physics}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\newcommand{\vvv}[1]{\textcolor{blue}{#1}}
%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}
\begin{document}

@@

\title{Blueprint for efficient nuclear spin characterization with color center}% Force line breaks with \\
%\thanks{A footnote to the article title}%

\author{Majid Zahedian}
 \affiliation{3rd Physical Institute University of Stuttgart, Germany}
 \affiliation{Institute of Quantum Electronics, ETH Z\"urich, Switzerland}%Lines b%Lines break automatically or can be forced with \\

\author{Vadim Vorobyov}
\email[]{v.vorobyov@pi3.uni-stuttgart.de}
 \affiliation{3rd Physical Institute University of Stuttgart, Germany}  
% with \\

\author{J\"org Wrachtrup}
 \affiliation{3rd Physical Institute University of Stuttgart, Germany}%Lines break 
 \affiliation{Max Planck Institute for solid state research, Stuttgart, Germany}%Lines break 
 %automatically or can be forced with \\ Third institution, the second for Charlie Author
